Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-30 article.tex
typo
Add reference for results
fix merge misstake
more precise

The top of Table \ref{tab:comparison} reports AUROC and AUPRC for all
four networks using in each case partial correlation with different
filtering functions. Except for the last two rows that use PCA, the
exact inverse of the covariance matrix was used in each case. These
results clearly show the importance of the filters. AUROC increases in
average from 0.77 to 0.93. PCA does not really affect AUROC scores but
it significantly improves AUPRC scores. Taking the average over
various parameter settings gives an improvement of 10\% in AUPRC but
only a minor change in AUROC. The last row (``Full method'') shows the
final performance of the method specifically tuned for the challenge
(see the Appendix \ref{app:optimized} for all details). Although this
tuning was decisive to obtain the best performance at the challenge,
it does not significantly improve neither AUROC nor AUPRC.

@@

Partial correlation and average partial correlation clearly outperform all
other methods. The improvement is more important in terms of AUPRC than in
terms of AUROC. As expected, Pearson correlation performs very poorly in terms
of AUPRC. GTE and GENIE3 work much better but these two methods are
nevertheless clearly below partial correlation. Among these two methods, GTE is
slightly better in terms of AUROC, while GENIE3 is significantly better in
terms of AUPRC. Given that we had to limit this latter method for computational
reasons, these results are very promising and a comparison with the full GENIE3
approach is certainly part of our future works.

>>>>

The top of Table \ref{tab:comparison} reports AUROC and AUPRC for all
four networks using in each case partial correlation with different
filtering functions. Except for the last two rows that use PCA, the
exact inverse of the covariance matrix was used in each case. These
results clearly show the importance of the filters. AUROC increases in
average from 0.77 to 0.93. PCA does not really affect AUROC scores but
it significantly improves AUPRC scores. Taking the average over
various parameter settings gives an improvement of 10\% in AUPRC but
only a minor change in AUROC. The last row (``Full method'') shows the
final performance of the method specifically tuned for the challenge
(see Appendix \ref{app:optimized} for all details). Although this
tuning was decisive to obtain the best performance at the challenge,
it does not significantly improve neither AUROC nor AUPRC.

@@

Partial correlation and averaged partial correlation clearly outperform all
other methods on all datatests (see Table \ref{tab:comparison} and Appendix \ref{app:supp}). The
improvement is more important in terms of AUPRC than in terms of AUROC. As
expected, Pearson correlation performs very poorly in terms of AUPRC. GTE and
GENIE3 work much better but these two methods are nevertheless clearly below
partial correlation. Among these two methods, GTE is slightly better in terms
of AUROC, while GENIE3 is significantly better in terms of AUPRC. Given that we
had to limit this latter method for computational reasons, these results are
very promising and a comparison with the full GENIE3 approach is certainly part
of our future works.
